### 2019-10-11 Manuscript/manuscript.tex
add more details about Superior Slave pole comparison that now cites Buchan2009a

Prior to the termination of the Trans-Hudson orogeny (before 1.8 Ga), I consider paleomagnetic poles with respect to the individual Archean provinces. There are poles in the compilation for the Slave, Wyoming, Rae, Superior and Nain provinces prior to Laurentia amalgamation. Overall, these data provide an opportunity to re-evaluate the paleomagnetic evidence for relative motions between Archean provinces prior to Laurentia assembly. A lingering question raised in \citet{Hoffman1988a} that still remains is to what extent the Archean provinces each had independent drift histories with significant separation or whether they have shared histories before experiencing fragmentation and remamalgamation. An analysis of the record strengthened with a new paleomagnetic pole from the Slave province in \cite{Mitchell2014a}, supports significant differential motion between the Superior and Slave provinces between 2.2 and 1.8 Ga. Following the termination of this orogeny (after 1.8 Ga), I consider poles from all the respective provinces and terranes to reflect the position of all of Laurentia.

>>>>

Prior to the termination of the Trans-Hudson orogeny (before 1.8 Ga), I consider paleomagnetic poles with respect to the individual Archean provinces. There are poles in the compilation for the Slave, Wyoming, Rae, Superior and Nain provinces prior to Laurentia amalgamation. Overall, these data provide an opportunity to re-evaluate the paleomagnetic evidence for relative motions between Archean provinces prior to Laurentia assembly. A lingering question raised in \citet{Hoffman1988a} that still remains is to what extent the Archean provinces each had independent drift histories with significant separation or whether they have shared histories before experiencing fragmentation and remamalgamation. The strongest comparison in this regard comes from comparisons between paleomagnetic poles between the Superior and Slave provinces \citep{Buchan2009a, Mitchell2014a}. High-quality paleomagnetic poles from these two provinces provide strong support for differential motion between the Superior and Slave provinces between 2.2 and 1.8 Ga with the two provinces not being in their relative orientation to one another either ca. 2.17 Ga \citep{Mitchell2014a} or ca. 2.02 Ga \citep{Buchan2009a}. These data provide paleomagnetic support for the hypothesis that the Trans-Hudson orogeny is the result of closure of an ocean basin between the Superior province and the Hearne+Rae+Slave provinces as the result of differential plate tectonic motion. Following the termination of this orogeny (after 1.8 Ga), I consider poles from all the respective provinces and terranes to reflect the position of all of Laurentia.
